True versus apparent shapes of astrophysical bow shocks

### 2015-06-23 papers/Paper1/sec-projection.tex
Paper1 - fix {array} envs and untrack .log, .pdf
23/06/15 update. Main content written.

\begin{equation}
\sin\phi_t = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
\end{equation}

@@

\begin{equation}
\left(\begin{array}{c}
x'_t \\ y'_t \\ z'_t
\end{array}\right)= R(\theta)\left(\begin{array}{c}
\cos\theta\cos i - \sin\theta\sin\phi_t \sin i \\
\sin\theta(1-\sin^2\phi_t)^{1/2} \\
\cos\theta\sin i +\sin\theta\sin\phi_t\cos i
\end{array}\right)
\end{equation}

>>>>

\begin{equation}
\sin\phi_t = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
\label{eq:tanphi}
\end{equation}

@@

\begin{equation}
\left(\begin{array}{c}
x'_t \\ y'_t \\ z'_t
\end{array}\right)= R(\theta)\left(\begin{array}{c}
\cos\theta\cos i - \sin\theta\sin\phi_t \sin i \\
\sin\theta(1-\sin^2\phi_t)^{1/2} \\
\cos\theta\sin i +\sin\theta\sin\phi_t\cos i
\end{array}\right)
\label{eq:tangential}
\end{equation}

It is important to note that the equation (\ref{eq:tanphi}) does not have a solution for arbitrary values for $\theta$ and $i$, since
it's required that $|\sin\phi_t|<1$. If $i\neq 0$, then, the  allowed values for $\theta$ are such that $\theta > \theta_\parallel$, where
$\theta_\parallel$ is given implicitly by:

\begin{align}
\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel |\tan i|)}
\label{eq:thetapar}
\end{align}

\subsection{Parallel and perpendicular projected shell radii}

Considering further applications to bow shocks, we will consider open shells. In order to compare the shell shape given by $R(\theta)$ with observations,
it is convenient to define the following apparent radii in the observer frame: $R'_\parallel$ and $R'_\perp$. These are projected distances of the shell tangent line
from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_\parallel = x'_t(y'_t=0)$
and $R'_\perp = y'_t(x'_t=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:

\begin{align}
R'_\parallel = R(\theta_\parallel)\cos(\theta + i) \label{eq:Rpar} 
\end{align}

Where $\theta_\parallel$ is the solution of equation (\ref{eq:thetapar}), and

\begin{align}
R'_\perp = R(\theta_\perp)\sin\theta_\perp\left(1-\sin^2(\phi_t(\theta_\perp))\right)^{1/2}
\end{align}

Where $\theta_\perp$ is the solution of the next implicit equation:

\begin{align}
\cot\theta_\perp = \frac{1-\left(1+\omega(\theta_\perp)^2\sin^22i\right)^{1/2}}{2\omega(\theta_\perp\cos^2 i)}
\end{align}
